%-------------------------
% Ryan Schachte Latex Resume
% Author : Ryan Schachte
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://ryan-schachte.com/}{\Large Ryan Schachte}} & Email : \href{mailto:code@ryan-schachte.com}{code@ryan-schachte.com}\\
  \href{http://ryan-schachte.com/}{http://www.ryan-schachte.com -- http://github.com/schachte} & Mobile : +1-480-452-8825 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Master of Science in Computer Science;  GPA: 3.82}{Dec. 2016 -- Dec. 2017}
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Bachelor of Science in Computer Science;  GPA: 3.78 }{Aug. 2013 -- Dec. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Connexta}{Phoenix, AZ}
      {Team Lead \& Software Engineer}{Oct 2016 - Present}
      \resumeItemListStart
        \resumeItem{DDF}
          {Open-source contributor involving security, data integration and feature work for the geo-spatial intelligence agency and other government contracts. Contributions made to our in-house open-source data integration framework known as DDF (Distributed Data Framework)}
        \resumeItem{Java \& Karaf}
          {Utilized Java 8, OSGI and the Karaf container environment to develop, deploy and manage our micro-service oriented architecture.  }
        \resumeItem{Jira \& Agile}
          { Working as a scrum master in a completely agile environment, we utilized tools such as Jira for ticket management, GitHub for repository control and code reviews and followed the Scrum framework.  }
      \resumeItemListEnd

    \resumeSubheading
      {ExxonMobil}{Houston, TX}
      {Software Engineer Co-Op}{Summer 2016 \& Fall 2017}
      \resumeItemListStart
        \resumeItem{Backend Platform Development}
          {Developed user-centered geophysical monitoring platform, utilizing Azure
PaaS resources, ASP.NET Core and Angular for the single-page front-end app. Platform will save 1000+ hours of
analysis annually through automation}
        \resumeItem{GIS}
          {Integrated real-time, interactive mapping component to track oil well pressures utilizing MapBox \& Leaflet.}
        \resumeItem{DevOps}
          {Scaled out \& implemented first usages of Chef into company infrastructure for managing oil wells at
scale. Automated the entire build and deployment process for oil well machines – Saving the company over 50
hours of manual labor per deployment.}
        
      \resumeItemListEnd

    \resumeSubheading
      {Allstate Insurance, CompoZed Labs}{Tempe, AZ}
      {Software Engineer Intern}{Sept. 2016 - May 2017}
      \resumeItemListStart
        \resumeItem{Cloud Application Development}
          {Created internal tools to manage company processes, project deadlines and
team assignments within the lab. Designed custom applications utilizing React/Redux with Node.JS backend and
Mongo DB. Pair programming, agile, sprint-based, test-driven development.}
      \resumeItemListEnd

    \resumeSubheading
      {IBM}{Austin, TX}
      {Software Engineer Intern}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Cloud Security}
          {Worked on Bluemix cloud security team developing beta edition of key protect, an encryption
management vault for encrypted secrets.}
        \resumeItem{Distributed Computing and Containers}
          {Designed custom scaling algorithms utilizing LXD containers, Linux,
Watchdog and Python. Integrated real-time monitoring for the SRE team using Sensu and Pager duty based on key
access volume.}
      \resumeItemListEnd
      
    \resumeSubheading
      {SimpleWan}{Phoenix, AZ}
      {Software Engineer Intern}{Fall 2015}
      \resumeItemListStart
        \resumeItem{PHP Backend Development}
          { Scaled out a variety of features for the custom WAN PaaS offered by SimpleWan
using the Symfony2 PHP web framework. Followed agile, test-driven development practices. Implemented beta
version of router dashboard to production which interfaced with firewall routers. Wrote custom API’s to
communicate to hardware routers.}
      \resumeItemListEnd

    \resumeSubheading
      {Intel}{Chandler, AZ}
      {Software Engineer Intern}{Summer 2015}
      \resumeItemListStart
        \resumeItem{Firmware Engineering}
          { Worked on XPoint memory architecture team. Implemented custom logging platform
into firmware to track failures within the bootloader. Developed automated bit error correction program that
scraped and organized firmware tests into excel sheets for the business on a daily interval.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Youtube Channel}
      {YouTube.Ryan-Schachte.com - Videos teaching Math and Comp Sci. Over 4500+ subscribers.}
    \resumeSubItem{Slack Emoji Bot}
      {Slack.Ryan-Schachte.com - Python CLI tool auto converts faces to slack emojis using convex hull.}
    \resumeSubItem{Bookium}
      {Bookium.Ryan-Schachte.com - Instantly downloads & transfers books to kindle from web-app in seconds.}
    \resumeSubItem{AirBnB Data Viz}
      {AirBnb.Ryan-Schachte.com - Data viz tool to analyze data trends for maximizing AirBnb profit.}
    \resumeSubItem{Android Food Recommendation App}
      {Android.Ryan-Schachte.com - Phone app that recommends food recipes
based on diet and physical activity. — More Projects on GitHub & YouTube!}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: Java, Python, Javascript, C\#, Node, HTML, CSS}
     \hfill
     \textbf{Technologies}{: AWS, React/Redux, Visual Studio, OSGI, Karaf, Docker, IntelliJ, VIM, Git, Chef, Django, Typescript, LXD, Linux}
    }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

